Blum axioms and nondeterministic computation of functions

### 2016-04-12 paper.tex
paper.tex: Add some results about Gödel numberings.

>>>>

There are several interesting properties we can show about acceptable Gödel numberings.
For instance,
if $\phi$ and $\phi'$ are any two such numberings,
there is a total recursive function that converts programs for $\phi$
into programs for $\phi'$;
that is, there is a total recursive function $f : \{0, 1\}^* \to \{0, 1\}^*$
such that, for every program $w$,
\begin{equation*}
    \phi_w = \phi'_{f(w)}.
\end{equation*}
To show this,
we can use the $\sigma$ function for $\phi'$
to fix the input program as the first variable of the $U$ function for $\phi$.
With a bit more work,
it is possible to make $f$ bijective \cite[p.~25]{Soare1987}.

Another important theorem is the recursion theorem
\cite[p.~181]{Rogers1987}.
It states that, if $\phi$ is any acceptable Gödel numbering
and $f$ is any total recursive function,
then there is some program $w_0$ such that $\phi_{w_0} = \phi_{f(w_0)}$.
That is,
if $f$ is any systematic transformation on programs,
there is a program $w$ (a fixed point for $f$) whose meaning under $\phi$ is unchanged.
The recursion theorem can be used,
for example, to show the existence of quines
(programs whose output are their own source codes)
in any Turing-complete programming language:
choose $f$ to be the function that, given a program $w$,
returns another program $f(w)$ that prints the string $w$ when run.
(For Turing machines, for instance,
we can encode the bits of $w$ in the transition table of $w$.)
Then, by the recursion theorem,
there is some program $w_0$ that is equivalent to its transformed version $f(w_0)$;
thus, $w_0$ already writes the string $w_0$, its own source code.
Therefore, any programming language has quines \cite[p.~227]{Kozen2006}.
